\section*{Professional Experience}
\begin{longtable}{L!{\VRule}R}
2017--Present&JP Morgan Chase \& Co: \textbf{Software Engineer}\\[5pt]
& \textit{Plato} \\[5pt]
& As a software engineer within an agile team on the firm's strategic risk reporting and management platform for credit derivitives, my work is split between backend and frontend design, developement and testing. \\[5pt]
& I am a recognised \textit{Application Security Champion} within the firm and am driving our team to deliver secure software and to keep up-to-date with security trends and vulnerabilities. \\[5pt]
& I have a reputation for excellence from both technology and business colleagues and frequently contribute to key architecural decisons for our application. \\[5pt]
& Also conduct interviews and review technical excercises for other prospective employees. \\[5pt]
& Technologies used: Python, Pandas, Django, AngularJS, REST, Jira, Git, Oracle Exadata, Jenkins, Linux\\[5pt]

2014--2017&University of Strathclyde: \textbf{Research Associate}\\[5pt]
& \textit{ADAPT}\\[5pt]
& Leading the design and development of software to automatically analyse large sets of time-series data for defect and anomoly detection. \\[5pt]
& This high-visibility international project involved collabarating with a prominent nuclear power generating firm and delivering both written and in-person updates to board-level senior stakeholders \\[5pt]
& I was hand-picked for this project due to my record of success in multidisciplinary research involving signal processing and software design. \\[5pt]
& Reduced processing time by 98\% when comparing the ADAPT software with the existing analysis methodology. \\ [5pt]
& Technologies used: Python, NumPy, Celery \\[5pt]
& \textit{cueART}\\[5pt]
& Lead developer on a team of 3, designing a signal acquisition and processing platform within LabVIEW. \\ [5pt]
& Needed to interface with hardware via MATLAB, C\#, and LabVIEW by writing custom adapters. CUDA C++ signal processing algorithms provided rapid imaging results. \\[5pt]
& I started porting key elements of this software to Python for maintainability reasons when I left this position. \\ [5pt]
& Technologies used: LabVIEW, MATLAB, C++, C\#, Python \\[5pt]
\end{longtable}